\section{Vision}
dot slash(TM) currently has a website in place for AutoMart for sale of used and new vehicles, including motorcycles and trucks. Users place their advertisements by entering textual data along with the vehicle images on the website. The system currently has a AI textual parser that takes the data and extrapolates relevant vehicle properties to create a valid advertisement. The advertisement consists of textual data representing vehicle details as well as images that contain vehicle being advertised. This data is entered into the existing AutoMart's database.

AutoMart currently faces spamming, poor image quality and misrepresentation problems. Spamming is caused by bots that upload irrelevant images to their system, causing many invalid advertisements. Currently there is no image inspection, which allows users to upload images of inferior quality, which may not result in an invalid advertisement but rather a bad one. Finally, they have a AI text parser which parser the textual data and generates relevant vehicle details which are used to represent the advertisement in the database. However they are facing a problem where the AI classifies the text data different from the image uploaded along with that data. This resulting in advertisement representing two different vehicles.

The aim is to solve this by implementing a subsystem that will prevent their system from allowing users and bots from uploading inferior quality and irrelevant images to their system.  The system also needs to ensure that the textual data and the image correspond to each other and in fact represent the same vehicle. Since they want to ensure the data matches the vehicle in the image, they wish to have certain vehicle details extrapolated from the image instead of extrapolating it from the text, which will reduce room for incorrect advertisements.